Cross Validation Approaches for Penalized Cox Regression

### 2018-05-11 main.tex
Change naming of gp and ungp in text

\section{Introduction}
Cox propotional hazard regression is one of the most commonly used statistical model for analyzing data with survival outcomes. Despite its popularity, Cox model is limited by its semiparametric nature: it is challenging to evaluate the model's predictive accuracy.

Suppose there are n subjects and m observed failure events. Use i for indexing observations, j for indexing events sorted by their failure time. For the ith subject, its covarites will be denoted by $X_{i}$; $\delta_{i}$ denotes whether the event is observed or not for this subject. $t_{j}$ denotes the failure time for the j th event; $t_{i}$ denotes the time observed for ith subject.  In the Cox model \citep{Cox1975}, the hazard function for an observation i is given by 
\begin{equation}h_{i}(t) = h_{0}(t) \text{exp}( X_{i}^{T} \beta)\end{equation} 
where $h_{0}$ is the baseline hazard and $e^{X_{i}^{T} \beta}$ is the relative risk. The estimation of the coefficients $\beta$s are obtained by maximizing the partial likelihood. For each individual subject, its contribution to the partial likelihood is 
\begin{equation} l_{i}(\beta) = \left \{\frac{\text{exp} ( X_{i}^{T} \beta)}{\sum_{ k \in R(t_{i})}\text{exp} ( X_{k}^{T} \beta)}\right \}^{\delta_{i}} \end{equation} \note{introduce notation $l_{i}$} , where $R(t_{i})$ denotes the set of observations at risk at time $t_{i}$.

For all n subjects, the partial likelihood is 
\begin{equation} L(\beta) =\prod_{i = 1}^{n} l_{i}(\beta) = \prod_{j=1}^{m} \frac{\text{exp} ( X_{j}^{T} \beta)}{\sum_{ k \in R(t_{j})}\text{exp} ( X_{k}^{T} \beta)}\end{equation}. As a semi-parametric model, Cox regression only gives estimations of the $\beta$ coefficients, without estimating the baseline hazard. Hence the interpretation of the Cox model is only valid in a relative sense.

@@

Selecting the tuning parameter $\lambda$ is crutial to getting LASSO estimations for $\beta$. The LASSO penality enforces sparcity to the regression model, so that it carries out an automatic variable selection along the solution path. As $\lambda$ increases, more coefficients would be set to 0 and fewer variables will be selected by the model. When $\lambda$ is too small, the model tends to be redundant. When $\lambda$ is too large, the model would be too conservative to select any variables. In either case, model's predictive accuray would be affected.

@@

%ZZZZZZZZZZZZZ
\par Currently, there are two common cross-validation approaches for Cox regression, both having its disadvantages. The most intuitive approach to conduct cross validation in Cox regression is i) fit the model to training set then ii) calculate cross-validated partial likelihood based on the observations from the test set as a measure for the model's predictive accuracy. As will be discussed in Section 2, this approach is unstable when number of events gets small. The second approach was propsoed by Verweij et al. \citep{Verweij1993}. This is a stablized version of cross-validated log likehood, which has been widely used and implemented in R packages such as $\tt{glmnet}$ \citep{glmnet}. Although this approach fixes the stability issue, it tends to yield more conservative models in practice. We hope to improve cross-validation procedure for Cox regression to achieve a good balance between stability and performance.

@@

  \subsection{Cross Validated Likelihood} 
Suppose a data set of n observations is split into K folds and the ith fold is left out, then a partial likelihood can be built over the K -1 folds and yields maximum likelihood estimates of the coefficients, denoted by $\hat{\beta}_{-i}$. An intuitive way to carry out cross validation is to use the partial likelihood on the test data as the cross validated error: \begin{equation}cvl = \sum_{i=1}^{K} l_{i}(\hat{\beta}_{-i})\end{equation} This is implemented in the $\tt{glmnet}$ package as the $\tt{ungrouped}$ option.

\par An alternative way to calculate cross-validated log likelihood was proposed by Verweij et al. They defined cross-validated log likelihood of leaving the ith fold out to be \begin{equation}cvl = \sum_{i=1}^{K} \{l(\hat{\beta}_{-i}) - l_{-i}(\hat{\beta}_{-i})\}. \end{equation} When the ith fold is left out, $l(\hat{\beta}_{-i})$ is the log partial likelihood evaluated at $\hat{\beta}_{-i}$ with all k folds of observations. $l_{-i}(\hat{\beta}_{-i})$ is the log partial likelihood evaluated at $\hat{\beta}_{-i}$ with observations from the other K-1 folds.

\par We refer to the first definition as ungrouped cross-validated partial likelihood (CVL) and the second definition as grouped cross-validated partial likelihood. The upper panels in Figure 2 illustrates the ideas of the two methods. The grouped CVL uses observations more efficiently than the ungrouped CVL. Since only the left-out fold would be used, the ungrouped CVL is unstable in practice when there are only very few observations in some folder.

@@

  \subsection{Cross Validated Deviance Residuals}
  %Need to update this section with the new baseline estimation method%
The fundamental challenge of conducting cross validation for cox regression is that the baseline hazard is not estimated from the model. Hence we proposed our second approach which involves estimating the actual baseline hazard $\hat{\Lambda}_{0}$. The sum of squares of Martingale residuals is a natural candicate for evaluating the model performance using baseline hazard. Martingale residuals and its normalized form, deviance residuals, were first proposed by \citep{Therneau1990} for Cox regression model diagnostics.

@@

As an alternative, the baseline hazard can also be estimated only based on the training set, leaving the test set as out-of-sample observations for calculating the residuals. There are two major issues with this approach. First, it would be common to run into situations where events in the test set occurred after the last event occured in the baseline, where the survival function dropped to 0. Unless those observations are treated as censored, this approach would not work. Second, there would be an extra numeric challenge for deviance residuals. Since the baseline hazard function $\hat{\Lambda}_{0}$ is a step function from 0, the cumulative hazard at the first time point from 0 is always 0. Since deviance residual contains a term $log(\delta_{i} - \hat{M}_{i})$, where $\delta_{i} - \hat{M}_{i} = \hat{\Lambda}_{0}$, this term would be negative infinity for the first time point and lead to a numeric issue for whichever fold that contains the first time point. Hence extra smoothing for the step function would be needed for this approach to work.

@@

  Simulation studies were conducted to compare how those methods behave relative to each other. We generated data with pre-specified baseline hazard, covariate matrix X, coefficient $\beta$ and censoring mechanism. Both low dimensional and high dimentional scenarios were examined. All cross-validation methods mentioned in Section 2 were applied to the data to select the tuning parameter $\lambda$ and produce $\hat{\beta}$ estimates. %Cross-validation were also compared to model selection criteria AIC and BIC.

@@

    \subsection {Simulations Comparing Cross-validation Approaches}
  %need to change figures to include the new cross-validated deviance residuals
   The simulation experiments were first conducted when the signal in the data was varied. In each simulated data set, there are n = 100 observations and p = 1000 covariates. 10$\%$ of the observations were censored. 10-fold cross-validation was implemented for all four methods. Number of non-zero $\beta$s was 20. The signal in the data set was varied by varing the magnitude of the $\beta$s from 0.50 to 1.50. For each scenario, 200 replications were used.

@@

\par Results of this simulation were illustrated in Figure 2.  The x axis of the plots are the magnitude of the non-zero $\beta$ coefficients. The left panel compares the $\lambda$ selected by different methods. The grouped cross-validated partial likelihood approach, which is currently most widely used approach, consistently selects $\lambda$s that are greater than the optimal one.  Greater $\lambda$ leads to greater penalties and fewer non-zero variables, hence the grouped approach is conservative in terms of selecting variables. While the proposed cross-validated Deviance residual has very close performance as the grouped approach, the ungrouped cross-validated log likelihood and the cross-validated linear predictor were more liberal than the other two methods. In general, all four methods tends to act conservatively and selects smaller models.

\par The right panel compares the MSE ratios of the model selected. The MSEs of the cross-validation selected models are compared with the MSE of the model given by the optimal $\lambda$. The y-axis represents the ratio of the two. The ungrouped method has the smallest MSE ratio. The linear predictor approach's performance is also very close the ungrouped appraoch. Both the grouped approach and the proposed deviance residual approach yield models that have greater MSE, hence are not recommended for use in practice.

\begin{table}[h]
\small
\centering
\caption{Simulations Comparing all four Cross-Validation methods, Varying n and p}
\begin{tabular}{llllllllllllllll}
\hline\\[-0.75em]
       & \multicolumn{3}{l}{n = 100, p = 20} &  & \multicolumn{3}{l}{n = 100, p = 100} &  & \multicolumn{3}{l}{n = 500, p = 10000} &  & \multicolumn{3}{l}{n = 250, p = 10000} \\
       & \multicolumn{3}{l}{$\#$of non-zero = 10} &  & \multicolumn{3}{l}{$\#$of non-zero = 10} &  & \multicolumn{3}{l}{$\#$of non-zero = 20} &  & \multicolumn{3}{l}{$\#$of non-zero = 20} \\ \cline{2-4} \cline{6-8} \cline{10-12} \cline{14-16} 
\hline\\[-0.75em]
       &     &        &MSE       &  &   &       & MSE     &    &    &        & MSE      &  &     &        & MSE      \\
       & $\lambda$ (SD)     & &Ratio       &  & 	$\lambda$ (SD)         & & Ratio     & &	$\lambda$ (SD)         & & Ratio      & &	 $\lambda$ (SD)         & & Ratio      
\\ 
\cline{2-2} \cline{4-4} \cline{6-6} \cline{8-8} \cline{10-10} \cline{12-12} \cline{14-14} \cline{16-16} 
\\[-0.75em]
Optimal &0.016 (0.009)&&/&&0.042 (0.003)&&/&&0.026 (0.001)&&/&&0.026 (0.001)&&/\\          
Grouped &0.035 (0.007)&&2.597&&0.073 (0.009)&&2.184&&0.053 (0.003)&&5.627&&0.123 (0.036)&&3.931\\
Ungrouped &0.030 (0.009)&&2.246&&0.064 (0.01)&&1.815&&0.040 (0.003)&&3.131&&0.070 (0.016)&&2.560\\
LinearPred &0.034 (0.007)&&2.559&&0.066 (0.008)&&1.880&&0.041 (0.003)&&3.350&&0.074 (0.016)&&2.713\\
DevResid &0.100 (0.009)&&14.005&&0.108 (0.008)&&4.087&&0.076 (0.003)&&9.133&&0.111 (0.028)&&3.767\\ 
\hline
\end{tabular}
\end{table}

\par Simulation studies were also conducted in scenarios with various sample sizes and dimensions. The results are shown in Table 1. While the ungrouped approach yields the smallest MSE and best predictive accuracy, the Linear Predictor and the Ungrouped approaches perform closely to each other across all settings. Grouped approach performs well in low-dimensions or with sufficient samples, while deviance residual approach performs better in high-dimensional settings.

@@

\par In this section, simulations studies were conducted to address the stability issue of the ungrouped cross-validated likelihood. The ungrouped approach is an intuitive way to carry out cross-validation. It also has the best predictive accuarcy based on the simulation results in previous sections. However, one big disadvantage of this approach is that it is unstable when number of observed events in some fold is really small. As is illustrated in Figure 3, when censoring increases or when number of folds increases, the model would fail to converge due to insufficient number of events in the test set. Hence, the ungrouped cross-validated likelihood should not be used when there is no sufficient number of events.

@@

    \subsection {Results of Leave-One-Out Cross Validation}
	\par In this section, Leave-One-Out Cross Validation (LOOCV) were studied, in comparison with 10-fold CV. When first introduced, the grouped cross-validated partial likelihood was proposed so that LOOCV for Cox regression became feasible. It is impossible to carry out LOO cross-validation using the ungrouped approach, because the partial likelihood cannot be built on the one left-out observation. While the grouped cross-validated partial likelihood solves the stability issue by aggregating more observations together, it is not an efficient way to evaluate the model fit. Simulation studies in Section 3.1 have illustrated that it tends to be conservative in variable selections and selects smaller models in various scenarios. This fact can be even more illustrated via the following simulation studies, where both 10-fold and LOOCV were conducted via grouped, linear predictor and deviance residual approaches and 10 fold CV was conducted for the ungrouped approach.
	\par As is illustrated in Figure 4, LOOCV selected models that have smaller MSE than 10-fold CV for all three CV approaches. As is shown in left and middle panels, LOOCV based on deviance residuals and grouped cross-validated partial likelihood still perform more conservatively than the ungrouped approach. Even if the grouped approach was proposed to allow LOOCV, the LOOCV based on the grouped approach does not surpass the 10-fold ungrouped approach. On the other hand, the Linear Predictors also allows LOOCV, and the LOOCV based on Linear Predictors performs better than the ungrouped approach.

@@

\begin{table}[h]
\centering
\caption{Application to Real Data Sets}
\label{my-label}
\begin{tabular}{llllll}
\hline
\\[-0.75em]
 & Ovarian & & & Shedden&  \\
& $\lambda$ & log($\lambda$) &  &$\lambda$  &  log($\lambda$)   \\ \cline{2-3} \cline{5-6} 
Grouped &0.1226 & -2.0985 && 0.1215 & -2.1079\\
Ungrouped & 0.0803 & -2.5222 && 0.0983 & -2.3197\\
Linear Pred &0.0828 & -2.4919 && 0.1013 & -2.2894\\
Dev Resid & 0.0992 & -2.3104 && 0.1110 & -2.1987\\ \hline
\end{tabular}
\end{table}

@@

\par How the CV methods perform on real data reflects what is shown in simulation studies. The ungrouped CVL is the most liberal approach. Deviance Residual and Grouped CVL approaches were both really conversative, while the ungrouped approach was the second liberal to ungrouped CVL. In Figure 5, the Cross Validated Error is rescaled and plotted for all four methods. A $\lambda$ will be selected when CVE curve reaches its lower point. The blue line, which represents the linear predictor approach, has more curvature near its lowest point. It is easier to pick out the minimum point for this blue curve. Hence this approach is better at picking out signals than the other three approaches. For the grouped cross-validated partial likelihood, there's almost no signal there.

\section{Discussion}
Four methods of conducting cross-validation for Cox Regression were compared through simulation studies in terms of their predictive accuracy. All cross-validation methods tend to select the more conservative model: with greater value of $\lambda$, and fewer variables selected into the model. Despite of the stability issue, the ungrouped approach is the most liberal one across all scenarios and yield the least MSE. The proposed linear predictor approach performs closely to the ungrouped approach. Under LOOCV, the linear predictor approach out-performs the ungrouped approach. Both the grouped approach and the proposed Deviance Residual approach perform conservatively, hence not recommended for use in practice. Results from real data application reflects results from the simulation studies.

>>>>

\section{Introduction}
Cox propotional hazard regression, since its original proposal in 1972, is by far the most common regression approach for analyzing survival data. Cox regression is built upon partial likelihood. Under the propotional hazard assumption, partial likelihood still preserves most properties of a full likelihood, while the estimation of the baseline can be skipped. Despite its popularity, Cox model is limited by this semiparametric nature: it is challenging to evaluate the model's predictive accuracy.

Suppose there are n subjects and m observed failure events. Use i for indexing observations, j for indexing events sorted by their failure time. For the i th subject, its covarites will be denoted by $X_{i}$; $\delta_{i}$ denotes whether an event is observed or not for subject i. $t_{i}$ denotes the time observed for subject i; $t_{j}$ denotes the failure time for the j th event.  In the Cox model \citep{Cox1975}, the hazard function for an observation i is given by 
\begin{equation}h_{i}(t) = h_{0}(t) \text{exp}( X_{i}^{T} \beta)\end{equation} 
where $h_{0}$ is the baseline hazard and $e^{X_{i}^{T} \beta}$ is the relative risk. The estimation of the coefficients $\beta$s is obtained by maximizing the partial likelihood. For each individual subject, its contribution to the partial likelihood is 
\begin{equation} l_{i}(\beta) = \left \{\frac{\text{exp} ( X_{i}^{T} \beta)}{\sum_{ k \in R(t_{i})}\text{exp} ( X_{k}^{T} \beta)}\right \}^{\delta_{i}} \end{equation} \note{introduce notation $l_{i}$} , where $R(t_{i})$ denotes the set of observations at risk at time $t_{i}$.

For all n subjects, the partial likelihood is constructed as a product of all individual contributed partial likelihood:
\begin{equation} L(\beta) =\prod_{i = 1}^{n} l_{i}(\beta) = \prod_{j=1}^{m} \frac{\text{exp} ( X_{j}^{T} \beta)}{\sum_{ k \in R(t_{j})}\text{exp} ( X_{k}^{T} \beta)}\end{equation}. As a semi-parametric model, Cox regression only gives estimations of the $\beta$ coefficients, without estimating the baseline hazard. Hence the interpretation of the Cox model is only valid in a relative sense.

@@

Selecting the tuning parameter $\lambda$ is crucial to getting LASSO estimations for $\beta$. The LASSO penalty enforces sparcity to the regression model, so that it carries out an automatic variable selection along the solution path. As $\lambda$ increases, more coefficients would be set to 0 and fewer variables will be selected by the model. When $\lambda$ is too small, the model tends to be redundant. When $\lambda$ is too large, the model would be too conservative to select any variables. In either case, model's predictive accuracy would be affected.

@@

%ZZZZZZZZZZZZZ
\par Currently, there are two common cross-validation approaches for Cox regression, both having its disadvantages. The most intuitive approach to conduct cross validation in Cox regression is i) fit the model to training set then ii) calculate cross-validated partial likelihood based on the observations from the test set as a measure for the model's predictive accuracy. As will be discussed in Section 2, this approach is unstable when number of events gets small. The second approach was proposed by Verweij et al. \citep{Verweij1993}. This is a stabilized version of cross-validated log likelihood, which has been widely used and implemented in R packages such as $\tt{glmnet}$ \citep{glmnet}. Although this approach fixes the stability issue, it tends to yield more conservative models in practice. We hope to improve cross-validation procedure for Cox regression to achieve a good balance between stability and performance.

@@

  \subsection{Cross Validated Likelihood} 
Suppose a data set of n observations is split into K folds and the ith fold is left out, then a partial likelihood can be built over the K -1 folds and yields maximum likelihood estimates of the coefficients, denoted by $\hat{\beta}_{-i}$. An intuitive way to carry out cross validation is to use the partial likelihood on the test data as the cross validated error: \begin{equation}cvl = \sum_{i=1}^{K} l_{i}(\hat{\beta}_{-i})\end{equation} This is implemented in the $\tt{glmnet}$ package as the $\tt{ungrouped}$ option. We refer to this definition as standard cross-validated partial likelihood.

\par An alternative way to calculate cross-validated log likelihood was proposed by Verweij and Van Houwelingen. They defined cross-validated log likelihood of leaving the ith fold out to be \begin{equation}cvl = \sum_{i=1}^{K} \{l(\hat{\beta}_{-i}) - l_{-i}(\hat{\beta}_{-i})\}. \end{equation} When the ith fold is left out, $l(\hat{\beta}_{-i})$ is the log partial likelihood evaluated at $\hat{\beta}_{-i}$ with all k folds of observations. $l_{-i}(\hat{\beta}_{-i})$ is the log partial likelihood evaluated at $\hat{\beta}_{-i}$ with observations from the other K-1 folds. We refer to this definition as Verweij and Van Houwelingen's cross-validated partial likelihood. This is implemented in the $\tt{glmnet}$ package as the default $\tt{grouped}$ option.

\par The upper panels in Figure 2 illustrates the ideas of the two methods. Through substraction, Verweij and Van Houwelingen's approach allows measuring individual observation's contribution to the partial likelihood, so that leave-one-out cross-validation is feasible. Since only the left-out fold would be used to construct the partial likelihood, the standard CVL is unstable in practice when there are only very few observations in some folder.

@@

  \subsection{Cross Validated Deviance Residuals}
  %Need to update this section with the new baseline estimation method%
The fundamental challenge of conducting cross validation for cox regression is that the baseline hazard is not estimated from the model. Hence we proposed our second approach which involves estimating the actual baseline hazard $\hat{\Lambda}_{0}$. The sum of squares of Martingale residuals is a natural candidate for evaluating the model performance using baseline hazard. Martingale residuals and its normalized form, deviance residuals, were first proposed by \citep{Therneau1990} for Cox regression model diagnostics.

@@

As an alternative, the baseline hazard can also be estimated only based on the training set, leaving the test set as out-of-sample observations for calculating the residuals. There are two major issues with this approach. First, it would be common to run into situations where events in the test set occurred after the last event occurred in the baseline, where the survival function dropped to 0. Unless those observations are treated as censored, this approach would not work. Second, there would be an extra numeric challenge for deviance residuals. Since the baseline hazard function $\hat{\Lambda}_{0}$ is a step function from 0, the cumulative hazard at the first time point from 0 is always 0. Since deviance residual contains a term $log(\delta_{i} - \hat{M}_{i})$, where $\delta_{i} - \hat{M}_{i} = \hat{\Lambda}_{0}$, this term would be negative infinity for the first time point and lead to a numeric issue for whichever fold that contains the first time point. Hence extra smoothing for the step function would be needed for this approach to work.

@@

  Simulation studies were conducted to compare how those methods behave relative to each other. We generated data with pre-specified baseline hazard, covariate matrix X, coefficient $\beta$ and censoring mechanism. Both low dimensional and high dimensional scenarios were examined. All cross-validation methods mentioned in Section 2 were applied to the data to select the tuning parameter $\lambda$ and produce $\hat{\beta}$ estimates. %Cross-validation were also compared to model selection criteria AIC and BIC.

@@

    \subsection {Simulations Comparing Cross-validation Approaches}
  %need to change figures to include the new cross-validated deviance residuals
   The simulation experiments were first conducted when the signal in the data was varied. In each simulated data set, there are n = 100 observations and p = 1000 covariates. 10$\%$ of the observations were censored. 10-fold cross-validation was implemented for all four methods. Number of non-zero $\beta$s was 20. The signal in the data set was varied by varying the magnitude of the $\beta$s from 0.50 to 1.50. For each scenario, 200 replications were used.

@@

\par Results of this simulation were illustrated in Figure 2.  The x axis of the plots are the magnitude of the non-zero $\beta$ coefficients. The left panel compares the $\lambda$ selected by different methods. Verweij and Van Houwelingen's cross-validated partial likelihood approach, which is currently most widely used approach, consistently selects $\lambda$s that are greater than the optimal one.  Greater $\lambda$ leads to greater penalties and fewer non-zero variables, hence Verweij and Van Houwelingen's approach is conservative in terms of selecting variables. While the proposed cross-validated Deviance residual has very close performance as Verweij and Van Houwelingen's approach, the standard cross-validated log likelihood and the cross-validated linear predictor were more liberal than the other two methods. In general, all four methods tends to act conservatively and selects smaller models.

\par The right panel compares the MSE ratios of the model selected. The MSEs of the cross-validation selected models are compared with the MSE of the model given by the optimal $\lambda$. The y-axis represents the ratio of the two. The standard method has the smallest MSE ratio. The linear predictor approach's performance is also very close the standard approach. Both Verweij and Van Houwelingen's approach and the proposed deviance residual approach yield models that have greater MSE, hence are not recommended for use in practice.

\begin{table}[h]
\small
\centering
\caption{Simulations Comparing all four Cross-Validation methods, Varying n and p}
\begin{tabular}{llllllllllllllll}
\hline\\[-0.75em]
       & \multicolumn{3}{l}{n = 100, p = 20} &  & \multicolumn{3}{l}{n = 100, p = 100} &  & \multicolumn{3}{l}{n = 500, p = 10000} &  & \multicolumn{3}{l}{n = 250, p = 10000} \\
       & \multicolumn{3}{l}{$\#$of non-zero = 10} &  & \multicolumn{3}{l}{$\#$of non-zero = 10} &  & \multicolumn{3}{l}{$\#$of non-zero = 20} &  & \multicolumn{3}{l}{$\#$of non-zero = 20} \\ \cline{2-4} \cline{6-8} \cline{10-12} \cline{14-16} 
\hline\\[-0.75em]
       &     &        &MSE       &  &   &       & MSE     &    &    &        & MSE      &  &     &        & MSE      \\
       & $\lambda$ (SD)     & &Ratio       &  & 	$\lambda$ (SD)         & & Ratio     & &	$\lambda$ (SD)         & & Ratio      & &	 $\lambda$ (SD)         & & Ratio      
\\ 
\cline{2-2} \cline{4-4} \cline{6-6} \cline{8-8} \cline{10-10} \cline{12-12} \cline{14-14} \cline{16-16} 
\\[-0.75em]
Optimal &0.016 (0.009)&&/&&0.042 (0.003)&&/&&0.026 (0.001)&&/&&0.026 (0.001)&&/\\          
V $\&$ VH &0.035 (0.007)&&2.597&&0.073 (0.009)&&2.184&&0.053 (0.003)&&5.627&&0.123 (0.036)&&3.931\\
Standard &0.030 (0.009)&&2.246&&0.064 (0.01)&&1.815&&0.040 (0.003)&&3.131&&0.070 (0.016)&&2.560\\
LinearPred &0.034 (0.007)&&2.559&&0.066 (0.008)&&1.880&&0.041 (0.003)&&3.350&&0.074 (0.016)&&2.713\\
DevResid &0.100 (0.009)&&14.005&&0.108 (0.008)&&4.087&&0.076 (0.003)&&9.133&&0.111 (0.028)&&3.767\\ 
\hline
\end{tabular}
\end{table}

\par Simulation studies were also conducted in scenarios with various sample sizes and dimensions. The results are shown in Table 1. While the standard approach yields the smallest MSE and best predictive accuracy, the Linear Predictor and the standard approaches perform closely to each other across all settings. Verweij and Van Houwelingen's approach performs well in low-dimensions or with sufficient samples, while deviance residual approach performs better in high-dimensional settings.

@@

\par In this section, simulations studies were conducted to address the stability issue of the standard cross-validated likelihood. The standard approach is an intuitive way to carry out cross-validation. It also has the best predictive accuracy based on the simulation results in previous sections. However, one big disadvantage of this approach is that it is unstable when number of observed events in some fold is really small. As is illustrated in Figure 3, when censoring increases or when number of folds increases, the model would fail to converge due to insufficient number of events in the test set. Hence, the standard cross-validated likelihood should not be used when there is no sufficient number of events.

@@

    \subsection {Results of Leave-One-Out Cross Validation}
	\par In this section, Leave-One-Out Cross Validation (LOOCV) were studied, in comparison with 10-fold CV. When first introduced, Verweij and Van Houwelingen's cross-validated partial likelihood was proposed so that LOOCV for Cox regression became feasible. It is impossible to carry out LOO cross-validation using the standard approach, because the partial likelihood cannot be built on the one left-out observation. While Verweij and Van Houwelingen's cross-validated partial likelihood solves the stability issue by aggregating more observations together, it is not an efficient way to evaluate the model fit. Simulation studies in Section 3.1 have illustrated that it tends to be conservative in variable selections and selects smaller models in various scenarios. This fact can be even more illustrated via the following simulation studies, where both 10-fold and LOOCV were conducted via Verweij and Van Houwelingen's approach, linear predictor and deviance residual approaches and 10 fold CV was conducted for the standard approach.
	\par As is illustrated in Figure 4, LOOCV selected models that have smaller MSE than 10-fold CV for all three CV approaches. As is shown in left and middle panels, LOOCV based on deviance residuals and Verweij and Van Houwelingen's cross-validated partial likelihood still perform more conservatively than the standard approach. Even if Verweij and Van Houwelingen's approach was proposed to allow LOOCV, the LOOCV based on Verweij and Van Houwelingen's approach does not surpass the 10-fold standard approach. On the other hand, the Linear Predictors also allows LOOCV, and the LOOCV based on Linear Predictors performs better than the standard approach.

@@

\begin{table}[h]
\centering
\caption{Application to Real Data Sets}
\label{my-label}
\begin{tabular}{llllll}
\hline
\\[-0.75em]
 & Ovarian & & & Shedden&  \\
& $\lambda$ & log($\lambda$) &  &$\lambda$  &  log($\lambda$)   \\ \cline{2-3} \cline{5-6} 
V $\&$ VH &0.1226 & -2.0985 && 0.1215 & -2.1079\\
standard & 0.0803 & -2.5222 && 0.0983 & -2.3197\\
Linear Pred &0.0828 & -2.4919 && 0.1013 & -2.2894\\
Dev Resid & 0.0992 & -2.3104 && 0.1110 & -2.1987\\ \hline
\end{tabular}
\end{table}

@@

\par How the CV methods perform on real data reflects what is shown in simulation studies. The standard CVL is the most liberal approach. Deviance Residual and Verweij and Van Houwelingen's CVL approaches were both really conversative, while the standard approach was the second liberal to standard CVL. In Figure 5, the Cross Validated Error is rescaled and plotted for all four methods. A $\lambda$ will be selected when CVE curve reaches its lower point. The blue line, which represents the linear predictor approach, has more curvature near its lowest point. It is easier to pick out the minimum point for this blue curve. Hence this approach is better at picking out signals than the other three approaches. For Verweij and Van Houwelingen's cross-validated partial likelihood, there's almost no signal there.

\section{Discussion}
Four methods of conducting cross-validation for Cox Regression were compared through simulation studies in terms of their predictive accuracy. All cross-validation methods tend to select the more conservative model: with greater value of $\lambda$, and fewer variables selected into the model. Despite of the stability issue, the standard approach is the most liberal one across all scenarios and yield the least MSE. The proposed linear predictor approach performs closely to the standard approach. Under LOOCV, the linear predictor approach out-performs the standardstandard approach. Both Verweij and Van Houwelingen's approach and the proposed Deviance Residual approach perform conservatively, hence not recommended for use in practice. Results from real data application reflects results from the simulation studies.
